% !TeX program = xelatex
\documentclass[11pt,a4paper,sans]{moderncv} % keep a valid base size

% ---- Slight size bump while staying moderncv-safe ----
\usepackage{anyfontsize}
\AtBeginDocument{%
  \fontsize{10pt}{12pt}\selectfont
  \recomputelengths
}

% ---- Theme ----
\moderncvstyle{classic}
\moderncvcolor{blue}
\nopagenumbers{}

% ---- Encoding & Layout ----
\usepackage[scale=0.90]{geometry}
\setlength{\hintscolumnwidth}{2.4cm}
\usepackage{enumitem}
\setlist[itemize]{topsep=3pt,itemsep=3pt,parsep=0pt,leftmargin=10pt}
\usepackage{ragged2e}

% ---- Emphasis macro (ATS-safe: bold text only) ----
\newcommand{\kw}[1]{\textbf{#1}}
\newcommand{\expsep}{\vspace{3pt plus 1pt minus 1pt}} % tweak 4pt as needed

% ---- Hanging-indent skill macro (used by Key & Technical Skills) ----
\newlength{\skilllabelwd}
\newcommand{\skill}[2]{%
  \par\noindent
  \hangindent=\dimexpr\skilllabelwd+1.2em\relax
  \hangafter=1
  \makebox[\skilllabelwd][l]{\textbf{#1}}%
  \hspace{1.2em}#2\par\vspace{2pt}
}

% ---- Identity ----
\name{Ankit} {Seal}
% \title{Architecting AI, IIoT \& Data Platforms from Edge to Cloud}
\address{Bristol, UK}
\phone[mobile]{+44 7454 361133}
\email{ankit.seal@gmail.com}
\social[linkedin]{ankitseal}
\extrainfo{LinkedIn: https://www.linkedin.com/in/ankitseal}

% ---- ATS-friendly PDF metadata (prefilled) ----
\makeatletter
\AtBeginDocument{%
  \hypersetup{
    pdftitle={Architecting AI, IIoT \& Data Platforms from Edge to Cloud},
    pdfauthor={Ankit Seal},
    pdfsubject={Curriculum Vitae},
    pdfkeywords={AI Solutions Architect, Industrial IoT, IIoT, OT/IT, Edge Computing, Cloud, OEE, Predictive Maintenance, Quality Analytics, Energy Optimisation, ISA-95, IEC 62443, ISO 27001, Node-RED, Docker, Siemens Insights Hub}
  }%
}
\makeatother

\begin{document}
\makecvtitle
\vspace*{-1.5\baselineskip} % tighten gap before the first section

% ---------- SUMMARY ----------
\section{Professional Summary}
\begin{justify}
Senior \kw{IoT Solution Architect} for \kw{Industry~4.0} delivering end-to-end \kw{IIoT}, \kw{edge}, and \kw{IT/OT convergence} from \kw{presales} and solution design through delivery, \kw{services \& governance}, and \kw{customer success}. I lead technical qualification and \kw{bid/tender}/\kw{RFP} responses, craft win-themes and \kw{SoW}s, and present tailored \kw{demos/PoCs} to ops leaders and \kw{CxO}s. I design scalable architectures integrating \kw{PLCs/SCADA/MES} with analytics platforms, normalising \kw{OPC UA}/\kw{MQTT}/\kw{Modbus} for \kw{OEE}, \kw{predictive maintenance}, and quality insights. I establish \kw{SLA/OLA} and \kw{MTTR} targets, and ensure reliable handovers with runbooks; post-deployment, I drive adoption via success plans, training, and renewals/expansion to maximise \kw{ARR} and measurable outcomes.
\end{justify}


% ---------- EXPERIENCE ----------
\section{Experience}
\cventry{2023--Present}{Senior Industrial IoT Applications Consultant \& Solutions Architect}{CAD-IT UK}{}{}{
\begin{itemize}
  \item \kw{Presales \& Solution Consulting:} Led technical qualification and discovery; authored multiple successful \kw{bids/tender} and \kw{RFP} responses; produced \kw{SoW}s, effort/cost estimates, and \kw{ROI} models; designed and presented tailored \kw{demos/PoCs} to operations leadership and \kw{CxO} stakeholders, driving solution confidence and buy-in.
  \item \kw{Qualification \& Discovery:} Ran stakeholder workshops to capture requirements, map current-state processes, and prioritise value cases; translated business goals into measurable success criteria and a delivery roadmap.
  \item \kw{System \& Architecture Design:} Defined \kw{IIoT} reference architectures, onboarding playbooks, and \kw{ISA-95} data models; established standards for \kw{IT/OT} connectivity and vendor integration.
  \item \kw{Data Strategy \& Analytics:} Designed pipelines to normalise \kw{OPC UA}/\kw{MQTT}/\kw{Modbus} telemetry and integrated historians/time-series data into \kw{Siemens Insights Hub}, enabling \kw{predictive maintenance}, \kw{OEE}, and quality insights.
  \item \kw{Scalability \& Performance:} Built containerised \kw{edge gateways} and services (\kw{Docker}, \kw{Node-RED}, \kw{Python}) for real-time, high-performance industrial data acquisition and analytics across \kw{hundreds of assets}.
  \item \kw{Services \& Governance:} Defined \kw{SLA/OLA} metrics (availability, \kw{MTTR}) for \kw{IIoT} services; chaired change-advisory review as an SME consultant.
  \item \kw{Delivery \& Change Management:} Coordinated production, IT, maintenance, and vendor teams to execute the plan; maintained solution documentation, \kw{runbooks}, and handover packs; facilitated knowledge transfer, cutover activities, and hypercare; aligned service \kw{SLA/OLA} expectations with operations.
\item \kw{Customer Success \& Value Realisation:} Built success plans with executives; tracked adoption and value KPIs; ran roadmap review meetings; delivered training and enablement; managed renewals and expansion opportunities to maximise \kw{ARR} and long-term outcomes.
  \item \kw{Strategic Partnership \& Outcomes:} Delivered an \kw{IIoT factory} solution for a \kw{global aerospace manufacturer}, enabling secure \kw{IT/OT convergence}, real-time analytics, and digital transformation in a complex manufacturing environment.
\end{itemize}
}\expsep

\cventry{2022--2023}{IT Solutions Technical Analyst}{Bristol Water}{}{}{
\begin{itemize}
  \item \kw{Automation \& Process Optimisation:} Designed and deployed \kw{RPA} bots to streamline workflows and reduce manual effort across functions.
  \item \kw{Data-Driven Decision Support:} Prototyped AI-enabled tools and IoT monitoring solutions, accelerating operational insights.
  \item \kw{Innovation \& Experimentation:} Produced proof-of-concepts (PoCs) to validate feasibility and value; documented outcomes and facilitated handovers to business stakeholders.
\end{itemize}
}\expsep

\cventry{2018--2021}{Technology Associate}{OneDot Automation}{}{}{
\begin{itemize}
  \item \kw{Product Development \& IP:} Invented and prototyped a patented \kw{wireless in-wall smart-home controller}; delivered privacy-focused automation (\kw{Node-RED}/\kw{Node.js}/openHAB).
  \item \kw{Real-time Tracking:} Engineered a real-time asset/staff tracking solution, integrating IPS with \kw{ESP32} (\kw{Embedded C++}) for reliable location telemetry.
  \item \kw{Medical Imaging AI:} Deployed a cloud \kw{U-Net} pipeline on \kw{Google Cloud Platform} for chest X-ray GGO detection; packaged inference for scalable use.
\end{itemize}
}\expsep

\cventry{2019--2022}{Lecturer (Part-time)}{University of the West of England}{}{}{
\begin{itemize}
  \item \kw{Teaching \& Labs:} Taught \kw{Computer Vision} fundamentals and led hands-on \kw{MATLAB} labs; created practical exercises that connected theory to real-world problem-solving.
\end{itemize}
}

% ---------- EDUCATION ----------
\section{Education}
\cventry{2021--2023}{MPhil.\ Research in Machine Vision}{University of the West of England}{}{}{
Thesis: \emph{3D Printed Object Authentication using Micro and Macro Surface Textures and Geometric}
}
\cventry{2016--2018}{MSc.\ Robotics}{University of Bristol}{}{}{Final Project: \emph{Indoor Localisation System using Low Power Bluetooth}}
\cventry{2013--2016}{BEng.\,(Hons) Electronics}{Anglia Ruskin University (Cambridge Campus)}{}{}{}


% ---------- CAREER HIGHLIGHTS & CERTIFICATIONS ----------
\section{Career Highlights \& Certifications}
\begin{itemize}
  \item Led a smart-factory digital transformation for a FTSE 250, multi-site UK retailer as part of a Continuous Improvement (CI) programme; deployed \kw{OEE} across multiple lines to drive operational excellence.
  \item Scaled \kw{IIoT} to \kw{350+ assets}, enabling real-time insights, remote monitoring, and diagnostics, contributing to cost savings of \kw{\textsterling{}3M+}.
  \item Delivered \kw{IIoT factory} deployment for a \kw{global aerospace manufacturer}, enabling secure \kw{IT/OT convergence}, advanced analytics, and digital transformation outcomes.
  \item Delivered end-to-end \kw{Siemens Insights Hub} deployments (architecture, edge acquisition, analytics, \kw{KPI dashboards}) across diverse manufacturing environments.
  \item Certified Associate: \kw{Siemens Insights Hub} Presales, Service, and Customer Success.
  \item Patent holder: \kw{Wireless in-wall smart-home controller} (IoT product design).
\end{itemize}

% ---------- KEY SKILLS ----------
\section{Key Skills}
% Set label width to the longest label in this section
\settowidth{\skilllabelwd}{\textbf{Stakeholder Leadership \& Collaboration}}

\skill{IT/OT Solution Architecture}{Design reference architectures and roadmaps for plant-to-enterprise integration (MES, SCADA, PLCs\,\(\leftrightarrow\)\,ERP/Cloud) aligned to \kw{ISA-95}.}
\skill{Smart Manufacturing \& CI}{Define use cases and deliver value realisation for \kw{OEE} improvement, \kw{predictive maintenance}, \kw{quality analytics}, and \kw{energy optimisation}.}
\skill{Operations Integration}{\kw{MES/SCADA/PLC} data modelling and interoperability; \kw{historian} integration; standards-based connectivity.}
\skill{Data Strategy, Analytics \& AI}{Apply \kw{ML} \& \kw{computer vision} for anomaly/predictive quality and edge inference; enable data-driven decisions at scale.}
\skill{Stakeholder Leadership \& Collaboration}{Facilitate cross-functional agreement on \kw{vision}, \kw{scope}, and \kw{priorities}; lead workshops, manage risks/issues, and unblock delivery via data-driven decisions and structured \kw{governance}.}
\skill{Delivery Excellence}{Drive rollouts through \kw{documentation}, knowledge transfer, \kw{hypercare}, and post-deployment support for long-term stability.}
\skill{Security \& Standards}{Working knowledge of \kw{IEC\,62443} and \kw{ISO\,27001} (risk-aware, security-by-design principles).}

% ---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
% Longest label used to set a consistent label width
\settowidth{\skilllabelwd}{\textbf{Observability \& Dev Practices}}

\skill{Platforms \& Cloud}{\kw{Siemens Insights Hub}; \kw{Google Cloud} (Compute/Storage/AI/ML); Azure IoT (IoT Hub/Edge exposure/PoCs).}\expsep
\skill{Edge \& Integration}{\kw{Edge gateways}; \kw{Docker}; \kw{Node-RED}; RESTful APIs; webhook integrations; \kw{OPC UA} clients/servers; \kw{MQTT} brokers.}\expsep
\skill{Web \& API}{Lightweight web apps (\kw{HTML}/JavaScript); back-end services in \kw{Node.js}/\kw{Python}; REST/JSON APIs \& SDKs; API tooling with \kw{Curl}/\kw{Postman}; documentation \& test collections.}\expsep
\skill{Identity \& Access}{\kw{JWT}-based service auth; role-based access across edge/cloud \kw{SSO} implementation.}\expsep
\skill{Industrial Connectivity}{\kw{OPC UA}, \kw{MQTT}, \kw{Modbus}, PROFINET, Ethernet/IP; PLC/DCS interfacing and OT data acquisition.}\expsep
\skill{Databases \& Storage}{\kw{MongoDB}; \kw{RAG} storage solution - vectorDB; time-series/\kw{historians}; cloud object storage; embedded DBs (e.g.\ SQLite).}\expsep
\skill{Programming \& ML}{\kw{Python}; \kw{SQL}; \kw{Node.js}/\kw{Node-RED}; \kw{MATLAB}; \kw{Embedded C++}; \kw{TensorFlow}, \kw{Keras}, \kw{PyTorch}; pandas, NumPy, scikit-learn.}\expsep
\skill{Computer Vision}{\kw{OpenCV}; scikit-image; classical \& deep CV pipelines; image pre-/post-processing.}\expsep
\skill{Data Engineering}{Python \kw{ETL}; batch/stream processing; schemas \& serialisation (\kw{JSON}, \kw{CSV}, Parquet); data validation \& QC.}\expsep
\skill{Observability \& Dev Practices}{\kw{Git}; logging/telemetry; API testing; container build workflows; basic CI pipelines.}\expsep
\skill{Visualisation}{Custom dashboards - \kw{Grafana}, \kw{PowerBI}; KPI \& time-series charting; \kw{Apache echarts}.}

\end{document}